---
title: "GW_Yerik_Analysis"
author: "Yilin Zhu"
date: "29/09/2016"
output: html_document
---

```{r Library, include=FALSE}
library(ggplot2)
library(reshape2)
library(grid)
library(scales)
library(sqldf)
library(rms)
library(pscl)
```

```{r Read Data, include = TRUE}
gjb <- read.csv('/Users/Yerik/OneDrive/UK/Imperial College/BA/Modules/MSF/MSF_GW_Group_5/Dataset/June 10-July 12, 2015 - Gaming, Jobs and Broadband - CSV.csv', stringsAsFactors = FALSE)
#View(gjb)
#summary(gjb)
```

### Demographic Data
```{r Descriptive Statistics, echo = TRUE, out.width = "60%", fig.align = "center"}
ggplot(data = gjb, aes(x=factor(sex, levels=c(1,2), labels = c("Male","Female"))))+geom_bar(stat="count")+labs(x="",y="No. of Respondents",title="Gender Distribution")

ggplot(data = gjb, aes(x=age))+geom_density()+labs(x="Age",title="Age Distribution")



for (i in 1:nrow(gjb)) {
  if (gjb[i,"age"] <= 35) gjb[i,"ageGroup"] <- 1
  if (gjb[i,"age"] > 35 & gjb[i,"age"] <= 50) gjb[i,"ageGroup"] <- 2
  if (gjb[i,"age"] > 50 & gjb[i,"age"] <= 65) gjb[i,"ageGroup"] <- 3
  if (gjb[i,"age"] > 65) gjb[i,"ageGroup"] <- 4
}

ggplot(data = gjb, aes(x=ageGroup))+geom_bar(stat="count")+labs(x="Age",title="Age Distribution")

ggplot(data = gjb, aes(x=factor(inc, levels=c(1:9,98,99), labels = c("<10","10-20","20-30","30-40","40-50","50-75","75-100","100-150",">150","Don't know","Refused"))))+geom_bar(stat="count")+labs(x="Income Range $'000",y="No. of Respondents",title="Income Distribution")

ggplot(data = gjb, aes(x=factor(race, levels=c(1,2,3,4,5,6,8,9), labels = c("White","Black","Asian/Islander","Mixed race","Native American","Other","Don't know","Refused"))))+geom_bar(stat="count")+labs(x="",y="No. of Respondents",title="Race Distribution")

ggplot(data = gjb, aes(x=factor(educ2, levels=c(1,2,3,4,5,6,7,8,98,99), labels = c("Less than High school","High school incomplete","High school","College no degree","Two year college","Bachelor","Postgrad no degree","Postgrad","Don't know","Refused"))))+geom_bar(stat="count")+labs(x="",y="No. of Respondents",title="Highest Education")

ggplot(data = gjb, aes(x=factor(marital, levels=c(1,2,3,4,5,6,8,9), labels = c("Married","Living with a partner","Divorced","Separated","Widowed","Never been married","Don't know","Refused"))))+geom_bar(stat="count")+labs(x="",y="No. of Respondents",title="Marital Status")

```

### Q1: What's the gender and age difference in online dating?

date1a: Have YOU, personally, ever used an online dating site such as Match.com, eHarmony, or OK Cupid?

```{r Dating1, echo = TRUE, out.width = "60%", fig.align = "center"}
date1a <- gjb[gjb[c("eminuse")]==1 | gjb[c("intmob")] ==1,] #extract the dataset for date1a
date1a <- date1a[date1a["date1a"] == c(1,2),] #remove the data of don't know and refused
ggplot(data = date1a)+geom_bar(aes(x=factor(date1a,levels=c(1,2),labels=c("Yes","No")),fill=factor(sex)),position="dodge",stat="count")+labs(x="Online Dating Sites Usage", y="No. of Respondents", title="Have you ever used an online dating site?")

date1a_test <- date1a[,c("sex","date1a")]
summary(date1a_test)
date1a_test$sex <- factor(date1a_test$sex,level=c(1,2),labels=c("Male","Female"))
date1a_test$date1a <- factor(date1a_test$date1a,level=c(1,2),labels=c("Yes","No"))
prop.test(table(date1a_test[,"sex"],date1a_test[,"date1a"]),alternative = "greater")

#reject H0 in 10%, there is a gender difference

#difference in age group
ggplot(data = date1a)+geom_bar(aes(x=ageGroup,fill=as.factor(date1a)),stat="count",position="stack") +labs(x="Age Group", y="", title="Percentage of Dating in Different Age Group")

date1a_test1 <- date1a[,c("ageGroup","date1a")]
summary(date1a_test1)
date1a_test1$sex <- as.factor(date1a_test1$ageGroup)
date1a_test1$date1a <- factor(date1a_test1$date1a,level=c(1,2),labels=c("Yes","No"))
prop.test(table(date1a_test1[,"ageGroup"],date1a_test1[,"date1a"]))

#reject H0, there is a difference among age group

date1a.age1 <- date1a[date1a["age"] < 50,]
p1 <- nrow(date1a.age1[date1a.age1["date1a"]==1,])/nrow(date1a.age1) #percent of dating in age<50
date1a.age2 <- date1a[date1a["age"] >= 50,]
p2 <- nrow(date1a.age2[date1a.age2["date1a"]==1,])/nrow(date1a.age2) #percent of dating in age>=50
date.age <- data.frame(age=c("<50",">=50"),percent=c(p1,p2))
ggplot(data = date.age)+geom_bar(aes(x=age,y=percent),stat="unique") +labs(x="Age Group", y="", title="Percentage of Dating in Different Age Group")
```

date2a: Have you ever used a dating app on your cell phone? 

```{r Dating2, echo = TRUE, out.width = "60%", fig.align = "center"}
date2a <- gjb[gjb[c("smart1")]==1,] #extract the dataset for date1a
date2a <- date2a[date2a["date2a"] == c(1,2),] #remove the data of don't know and refused
ggplot(data = date2a)+geom_bar(aes(x=factor(date2a,levels=c(1,2),labels=c("Yes","No")),fill=factor(sex)),position="dodge",stat="count")+labs(x="Online Dating Sites Usage", y="No. of Respondents", title="Have you ever used a dating app?")

date1a.age1 <- date1a[date1a["age"] < 50,]
p1 <- nrow(date1a.age1[date1a.age1["date1a"]==1,])/nrow(date1a.age1) #percent of dating in age<50
date1a.age2 <- date1a[date1a["age"] >= 50,]
p2 <- nrow(date1a.age2[date1a.age2["date1a"]==1,])/nrow(date1a.age2) #percent of dating in age>=50
date.age <- data.frame(age=c("<50",">=50"),percent=c(p1,p2))
ggplot(data = date.age)+geom_bar(aes(x=age,y=percent),stat="unique") +labs(x="Age Group", y="", title="Percentage of Dating in Different Age Group")
```

#### Conclusion: 

- There IS a gender difference found in online dating.
- The percentage of dating in age group <50 is the two times that of dating in age group >=50.


### Q2: Opinions about online dating

- "Online dating is a good way to meet people"
- "Online dating allows people to find a better match for themselves because they can get to know a lot more people"
- "People who use online dating sites are desperate" (colour)
- "Online dating keeps people from settling down because they always have options for people to date" (colour)
- "Online dating is easier and more efficient than other ways of meeting people"
- "Online dating is more dangerous than other ways of meeting people")

```{r Dating Opinion, echo = TRUE, out.width = "60%", fig.align = "center"}
date <- gjb[c("date4a","date4b","date4c","date4d","date4e","date4f")]
mdate <- melt(date, id.vars = 0)
mdate$value <- factor(mdate$value,levels=c(1,2,8,9),labels=c("Agree","Disagree","Don't know","Refused"))
ggplot(data = mdate, aes(x=variable,fill=value))+geom_bar(stat = "count")+labs(x="Question",y="No. of Responds",title="Distribution of Opinions about Online Dating")
```

Opinions in people who had no experience in online dating

```{r Dating Opinion1, echo = TRUE, out.width = "60%", fig.align = "center"}
date1a_no <- gjb[gjb["date1a"] == 2,c("date4a","date4b","date4c","date4d","date4e","date4f")]
date1a_no <- na.omit(date1a_no)
mdate4_no <- melt(date1a_no[,c("date4a","date4b","date4c","date4d","date4e","date4f")], id.vars = 0)
ggplot(data = mdate4_no, aes(x=variable,fill=factor(value,levels=c(1,2,8,9),labels=c("Agree","Disagree","Don't know","Refused"))))+geom_bar(stat = "count")+labs(x="Question",y="No. of Responds",title="Said No about Online Dating")
```

Opinions in people who had experience in online dating

```{r Dating Opinion2, echo = TRUE, out.width = "60%", fig.align = "center"}
date1a_yes <- gjb[gjb["date1a"] == 1,c("date4a","date4b","date4c","date4d","date4e","date4f")]
date1a_yes <- na.omit(date1a_yes)
mdate4_yes <- melt(date1a_yes[,c("date4a","date4b","date4c","date4d","date4e","date4f")], id.vars = 0)
ggplot(data = mdate4_yes, aes(x=variable,fill=factor(value,levels=c(1,2,8,9),labels=c("Agree","Disagree","Don't know","Refused"))))+geom_bar(stat = "count")+labs(x="Question",y="No. of Responds",title="Said Yes about Online Dating")
```

#### Conclusion: 

It seems that both group of people are concerned about the safety issue with online dating.

### Q3: What's the gender and age difference in gaming? (excluded)

game1: Do you ever play video games on a computer, TV, game console, or portable device like a cell phone?

```{r Gaming, echo = TRUE,out.width = "60%", fig.align = "center"}
game1 <- gjb[gjb["game1"] == c(1,2),]

#Overall
ggplot(data = game1)+geom_bar(aes(x=factor(game1,levels=c(1,2),labels=c("Yes","No"))),position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Have you ever played video games?")

#Gender
ggplot(data = game1)+geom_bar(aes(x=factor(game1,levels=c(1,2),labels=c("Yes","No")),fill=factor(sex)),position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Have you ever played video games?")

#Age
ggplot(data = game1)+geom_bar(aes(x=factor(game1,levels=c(1,2),labels=c("Yes","No")),fill=factor(age)),position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Have you ever played video games?")

game1.age1 <- game1[game1["age"]<50,]
game1.age2 <- game1[game1["age"]>=50,]
ggplot(data = game1.age1)+geom_bar(aes(x=factor(game1,levels=c(1,2),labels=c("Yes","No"))),position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Have you ever played video games?")
ggplot(data = game1.age2)+geom_bar(aes(x=factor(game1,levels=c(1,2),labels=c("Yes","No"))),position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Have you ever played video games?")

#Proportion test (H0: There is no gender difference in the distribution of playing or not playing game in population)
game1_test <- gjb[gjb["game1"] == c(1,2),c("sex","game1")]
summary(game1_test)
game1_test$sex <- factor(game1_test$sex,level=c(1,2),labels=c("Male","Female"))
game1_test$game1 <- factor(game1_test$game1,level=c(1,2),labels=c("Yes","No"))
prop.test(table(game1_test[,"sex"],game1_test[,"game1"]),alternative = "greater")
#There is a gender difference among gaming people
```

game3: 
- "Most people who play video games are men"
- "People who play violent video games are more likely to be violent themselves"

```{r Gaming1, echo = TRUE,out.width = "60%", fig.align = "center"}
game3 <- gjb[c("game3a","game3b")]
mgame3 <- melt(game3, id.vars = 0)
mgame3$value <- factor(mgame3$value,levels=c(1,2,8,9),labels=c("Agree","Disagree","Don't know","Refused"))
ggplot(data = mgame3, aes(x=variable,fill=value))+geom_bar(stat = "count")+labs(x="Question",y="No. of Responds",title="Distribution of Opinions about Gaming")
ggplot(data = mgame3, aes(x=variable,fill=value))+geom_bar(stat = "count",position="dodge")+labs(x="Question",y="No. of Responds",title="Distribution of Opinions about Gaming")
```

game4:
"Some people use the term “gamer” to describe themselves as a fan of gaming or a frequent game player. Do you think the term “gamer” describes you well, or not?"

```{r Gaming2, echo = TRUE,out.width = "60%", fig.align = "center"}
game4 <- gjb[gjb[c("game1")]==1,]
game4 <- game4[game4["game4"]==c(1,2),]
ggplot(data = game4, aes(x=factor(game4,levels=c(1,2),labels=c("Yes","No"))))+geom_bar(position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Are you a 'gamer'?")
ggplot(data = game4, aes(x=factor(game4,levels=c(1,2),labels=c("Yes","No")),fill=factor(sex)))+geom_bar(position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Are you a 'gamer'?")
```

#### Conclusion:
- 1 There is a gender difference in gaming population.
- 2 There is a age difference in gaming population (people <50 tend to play more gaming).
- 3 Among people who play game, they tend to avoid call themselves "gamer" but men tend to do so than women do.

### Q4: The relationship between gaming and dating (excluded)

```{r Gaming and Dating, echo = TRUE,out.width = "60%", fig.align = "center"}
#gaming/non-gaming people who did or didn't have online dating
a <- nrow(game4[game4[,"date1a"]==1,])/nrow(game4) #dating Yes / gaming
b <- nrow(game4[game4[,"date1a"]==2,])/nrow(game4) #dating No / gaming
game4_n <- gjb[gjb[c("game1")]==2,]
c <- nrow(game4_n[game4_n[,"date1a"]==1,])/nrow(game4_n) #dating Yes / no-gaming
d <- nrow(game4_n[game4_n[,"date1a"]==2,])/nrow(game4_n) #dating No / no-gaming
gd <- data.frame(type=c("date/gaming","date/non-gaming"),percent=c(a,c))
ggplot(data=gd, aes(x=type,y=percent))+geom_bar(stat="unique")
mat <- matrix(c(a,b,c,d),byrow=F,nrow=2)
colnames(mat) <- c("Gaming","Non-Gaming")
rownames(mat) <- c("Dating","Non-Dating")
#chisq.test(mat)
gd_test <- gjb[gjb["game1"] == c(1,2) & gjb["date1a"] ==c(2),c("date1a","game1")]
gd_test <- na.omit(gd_test)
summary(gd_test)
gd_test$game1 <- factor(gd_test$game1,level=c(1,2),labels=c("Game","Non-Gaming"))
gd_test$date1a <- factor(gd_test$date1a,level=c(2),labels=c("Non-Dating"))
chisq.test(table(gd_test[,"date1a"],gd_test[,"game1"]))
#not sure this chisq.test was used correctly
```

#### Conclusion:

- 1 Non-gaming population has a higer percentage of online dating.
- 2 The percentage of people who had no online dating is similar among gaming and non-gaming population

### Q5: The Impact of Demographic Data on Online Dating

```{r Logistic Regression, echo = TRUE,out.width = "60%", fig.align = "center"}
#Gender, Race, Highest Education, Marital status, Age, Income; impact on dating
date1_logit <- gjb[gjb[c("eminuse")]==1 | gjb[c("intmob")] ==1,c("date1a","sex","race","educ2","marital","age","inc")]
date1_logit <- date1_logit[date1_logit["date1a"] == c(1,2),]

date1_logit$date1a[which(date1_logit["date1a"]==2)] <- 0
date1_logit$date1a[which(date1_logit["sex"]==2)] <- 0
date1_logit$race[which(date1_logit["race"]>1) & which(date1_logit["race"]<9)] <- 0
date1_logit$race[which(date1_logit["race"]==9)] <- NA
for (i in 1:nrow(date1_logit)) {
  if (date1_logit[i,"age"] <= 35) date1_logit[i,"age"] <- 1
  if (date1_logit[i,"age"] > 35 & date1_logit[i,"age"] <= 50) date1_logit[i,"age"] <- 2
  if (date1_logit[i,"age"] > 50 & date1_logit[i,"age"] <= 65) date1_logit[i,"age"] <- 3
  if (date1_logit[i,"age"] > 65) date1_logit[i,"age"] <- 4
}

for (i in 1:nrow(date1_logit)) {
  for (j in 1:ncol(date1_logit)) {
  if (date1_logit[i,j] == 98 | date1_logit[i,j] == 99) date1_logit[i,j] <- NA
  }
}

summary(date1_logit)
ggplot(data = date1_logit, aes(x=age))+geom_bar(stat="count")
mylogit1 <- glm(date1a~sex+race+educ2+marital+age+inc,data=date1_logit,family = "binomial")
summary(mylogit1)
pR2(mylogit1)
mylogit2 <- glm(date1a~sex+race+educ2+marital+inc,data=date1_logit,family = "binomial")
summary(mylogit2)
pR2(mylogit2)

```

#### Conclusion:

- 1 Gender has little effect on determining whether a person had online dating or not.
- 2 Race, education, maritial status and income all have significant statistical effects on determining whether a person had dating or not; marital status is the most significant factor. (but I'm confused in interpreting the model, will discuss you later)